Determinism, Complexity, and Predictability in Computer Performance

### 2014-04-11 wpe.tex
clean up haven paragraph, use different WPE vs MASE image

As a final note: there has been prior work under a similar title to
ours~\cite{haven2005}, but there are only superficial similarities
between the two research projects.  Haven {\sl et al.} utilize the
relative entropy to quantify how much better a distribution over
system states evolved from small ensembles to predict the future of a
dynamical system compared to its asymptotic distribution. Our work
quantifies the predictability of a single observed time series using
weighted permutation entropy and makes no assumptions about the
underlying dynamics. {\color{red} These approaches are very different:
  Haven's compares two distributions, the average behavior versus the
  behaviors that can be seen given a reasonably known state in the
  past; ours attempts to quantify how well an appropriate predictor
  will do for a given time-series without any understanding of how
  that time-series was generated. [[Seems to me like the first part of
      this paragraph made the point.  Is this second set of stuff
      needed?]]}

>>>>

As a final note: there has been prior work under a similar title to
ours~\cite{haven2005}, but there are only superficial similarities
between the two research projects.  Haven {\sl et al.} utilize the
relative entropy to quantify how much better one can predict the exact
state of a system from a distribution over system states evolved from 
a small ensemble around a prior known exact state, verses its asymptotic
distribution, requiring a model to perform the evolution. Our work
quantifies the predictability of a single observed time series using
weighted permutation entropy and makes no assumptions about the
underlying dynamics.
